02-preliminary-analysis

### 2024-05-25 data/02-preliminary-analysis.qmd
Experiments profiling the neighborhoods based on their accessibility characteristics

care_dest <- care_dest |> rename("care_ID" = "ID") |> mutate(care_ID = as.character(care_ID)) 
```
```{r}
care_dest|> st_drop_geometry() |> group_by(Care_Category) |> summarise(count = n())
```

@@

Aggregating time!
```{r}
#ID = care destination ID (in care_dest), GeoUID is id of the DA, from_id is parcel ID
saveRDS(access_15, "access_15.rds")
```

>>>>

care_dest <- care_dest |> rename("care_ID" = "ID") |> mutate(care_ID = as.character(care_ID)) 
```

```{r}
care_dest|> st_drop_geometry() |> group_by(Care_Category) |> summarise(count = n())
```

@@

Aggregating time!
```{r}
#ID = care destination ID (in care_dest), GeoUID is id of the DA, from_id is parcel ID
save(access_15, file = "access_15.rda", compress = "xz")
```
